Smart Model Elimination for Efficient Automated Machine Learning in Healthcare

### 2024-06-27 paper/paper.tex
Update paper.tex

Machine learning (ML) algorithms require complicated processes like hyperparamater tuning, and can be modified in conjunction with one another, like in ensemble learning. To do this on a larger scale and at greater speeds, recent research and effort have been put into developing AutoML frameworks. These frameworks create comfortable environments for models to excel in. They handle missing values, preprocess data, and optimize training to ensure the best results [1].

@@

Several observations were made from running these datasets. First, accuracy did not change for 4 of the 6 benchmarks. The other two benchmarks on eye states and diabetes prediction represented a loss of accuracy for SMEML by 0.13\% and 1.95\%, respectively. Training time, however, favored SMEML in every trial. SMEML outperformed the dummy framework by 173.96 seconds in its worst performance on the lung cancer trial and by 383.94 seconds in its best performance on the eye state dataset. Relative to the dummy's performance, a percent decrease in time to run for SMEML of at least 46.78\% could be seen, with a decrease of up to 69.22\% observerd as well. SMEML's worst performance by percent decrease was also the performance in which it returned perfect accuracy. 
\section{Discussion}
\subsection{Summary}
SMEML consistently achieves comparable accuracy to its dumb counterpart while significantly reducing the time required to train the model. Notably, SMEML's performance is not limited by the size of the dataset, achieving its best runtimes--first, third, and fourth fastest overall--on 'large' datasets (those exceeding 1000 rows). SMEML also chose less common algorithms, such as selecting SGDClassifier for the Pima Indians Diabetes Dataset [19] rather than defaulting to industry-standard boosting algorithms [23]. This efficiency and versatility is important in third world medicine where there is a constant influx of new patient data that must be processed quickly. A practical demonstration of this software's real-world application can be found on our SmartDx website [24]. Source code can be found at [25].
\subsection{Limitations}
Our implementation of SMEML has limitations. These include a small training set due to lack of available datasets, finite computing power, time constraints, and a lack of access to paticular scientific literature. Our framework only improves on the model selection process and does not address the various other aspects of AutoML. Therefore, SMEML is not comparable to other full-featured AutoML frameworks.
\subsection{Future Work}
Future work will include increasing the size of the training set, implementing a fully fledged AutoML framework, and conducting a detailed experiment comparing SMEML to other popular AutoML frameworks. Furthermore, we will examine other types of machine learning such as regression and multiclass-classification.

>>>>

Machine learning (ML) algorithms require complicated processes like hyperparamater tuning, and can be modified in conjunction with one another, like in ensemble learning. To do this on a larger scale and at greater speeds, recent research and effort have been put into developing AutoML frameworks. These frameworks create comfortable environments in which models can excel. They handle missing values, preprocess data, and optimize training to ensure the best results [1].

@@

The first observation made was that accuracy did not change for 4 of the 6 benchmarks. The other two benchmarks on eye states and diabetes prediction represented a loss of accuracy for SMEML by 0.13\% and 1.95\%, respectively. Training time, however, favored SMEML in every trial. SMEML outperformed the dummy framework by 173.96 seconds in its worst performance on the lung cancer trial and by 383.94 seconds in its best performance on the eye state dataset. Relative to the dummy's performance, a percent decrease in time to run for SMEML of at least 46.78\% could be seen, with a decrease of up to 69.22\% observerd as well. SMEML's worst performance by percent decrease was also the performance in which it returned perfect accuracy. 
\section{Discussion}
\subsection{Summary}
SMEML consistently achieves comparable accuracy to its dumb counterpart while significantly reducing the time required to train the model. Notably, SMEML's performance is not limited by the size of the dataset, achieving its best runtimes--first, third, and fourth fastest overall--on 'large' datasets (those exceeding 1000 rows). SMEML also chose less common algorithms, such as selecting SGDClassifier for the Pima Indians Diabetes Dataset [19] rather than defaulting to industry-standard boosting algorithms [23]. This efficiency and versatility is important in third world medicine where there is a constant influx of new patient data that must be processed quickly. A practical demonstration of this software's real-world application can be found on our SmartDx website [24]. Source code can be found at [25].
\subsection{Limitations}
Our implementation of SMEML has limitations. These include a small training set due to lack of available datasets, finite computing power, time constraints, and a lack of access to paticular scientific literature. Our framework only improves on the model selection process and does not address the various other aspects of AutoML. Therefore, SMEML is not comparable to other full-featured AutoML frameworks.
\subsection{Future Work}
Future work will include increasing the size of the training set, implementing a fully fledged AutoML framework, and conducting a detailed experiment comparing SMEML to other popular AutoML frameworks.
